General constraints on magic distillation protocols from statistical mechanics

### 2021-06-05 magic_paper.tex
minor corrections and comment additions

	The expression follows from the definition of $\Gamma_{\bma}$ which gives
	\begin{equation}
		\Gamma_{\bma}(\w) = \bigoplus_{i=1}^N w_i (1/a_i, 1/a_i, \dots, 1/a_i).
	\end{equation}
	This directly leads to
	\begin{align}
		H_\alpha(\Gamma_{\bma}(\w)) &= \frac{1}{1-\alpha} \log_2 \sum_{i=1}^N a_i \left( \frac{w_i}{a_i} \right)^\alpha \nonumber\\
		&= \frac{1}{1-\alpha} \log_2 \sum_{i=1}^N w_i^{\alpha} a_i^{1-\alpha} \nonumber\\
		&= \frac{1}{1-\alpha} \log_2 K^{1-\alpha} \sum_{i=1}^N w_i^{\alpha} \nonumber\\
		&= K + \frac{1}{1-\alpha} \log_2 \sum_{i=1}^N w_i^{\alpha} r_i^{1-\alpha} \nonumber\\
		&= K - D_\alpha(\w ||\r).
	\end{align}
\end{proof}

@@

1. \nick{looks true numerically, maybe can use~\cref{thm:H2D}}

2. Assume $D_\alpha (\rho,\tau) = 0$.
Then,
\begin{equation}
	\sum_{\bmx} W_{\tau}(\bmx) \left( \frac{W_\rho(\x)}{W_\tau(\x)} \right)^\alpha = 1,
\end{equation}
\nick{so...}.
The converse holds by inspection.

3. This property follows from the multiplicativity of the WIgner distribution.
In particular,
\begin{align}
	&D_\alpha(\rho^{\otimes n} || \tau^{\otimes n}) = \nonumber\\
	&\frac{1}{\alpha - 1} \log_2 \sum_{\bmx} W_{\rho^{\otimes n}}(\bmx)^\alpha W_{\tau^{\otimes n}}(\bmx)^{1-\alpha} = \nonumber\\
	&= n D_{\alpha}(\rho || \tau). \nick{complete steps}
\end{align}

4. \nick{This must hold due to~\cref{thm:H2D}}
\end{proof}

@@

For the given form of $\alpha$, $H_{\alpha}$ is Schur-concave due to~\cref{thm:HSchur}, so
\begin{equation}
	H_{\alpha}(\Gamma_{\bma}(W_{\rho_n})) \leq H_{\alpha}(\Gamma_{\bma'}(W_{\rho'_{n'}})),
\end{equation}
and we can use~\cref{thm:H2D} to rewrite the inequality as
\begin{equation}
	K - D_{\alpha}(W_{\rho_n} || W_{\tau_n}) \leq K - D_{\alpha}(W_{\rho'_{n'}} || W_{\tau'_{n'}}),
\end{equation}.
Due to~\cref{thm:Da_props}, we can rewrite the inequality as
\begin{equation}
	K - nD_{\alpha}(W_{\rho} || W_{\tau_n}) \leq K - n'D_{\alpha}(W_{\rho'} || W_{\tau'_{n'}}),
\end{equation}
and then it is clear that we can rearrange it to
\begin{equation}
	\frac{n'}{n} \leq \frac{D_{\alpha}(\rho||\tau)}{D_{\alpha}(\rho'||\tau')}.
\end{equation}
\end{proof}

@@

Conversely, suppose $\rho$ has negativity in its Wigner representation. This implies that $\sum_{\x} |W_\rho (\x)| >1$. We now consider $\sum_{\x} W_\rho (\x)^{a/b}$ for $a/b >1$ and $a$ even and $b$ odd. We have that
\begin{align}
\sum_{\x} W_\rho (\x)^{a/b} &= \sum_{\x} |W_\rho (\x)|^{a/b} \nonumber \\
&= \sum_{\x} |W_\rho (\x)|^{1+ \epsilon},
\end{align}
where $\epsilon = a/b - 1 >0$. By choosing $a$ and $b$ appropriately we can make $\epsilon$ arbitrarily close to $0$ and therefore there exists a sequence $\epsilon_n$ such that
\begin{equation}
\sum_{\x} |W_\rho (\x)|^{1+ \epsilon_n} \rightarrow \sum_{\x} |W_\rho (\x)| >1.
\end{equation}
Therefore, $H_\alpha (W_\rho (\x)) <0 $ at some point in the sequence, which completes the proof.
\end{proof}
Therefore Wigner negativity coincides with negativity in at least one Renyi entropy.
\ddd{[Looking at this limit it almost feels like the $\alpha \rightarrow 0$ limit is actually giving mana....modulo the technical problem of taking the limit without calculus. I will think more about this point.]}
\subsubsection{Extention to general relative majorization}

>>>>

	The expression follows from the definition of $\Gamma_{\bma}$ which gives
	\begin{equation}
		\Gamma_{\bma}(\w) = \bigoplus_{i=1}^N w_i (1/a_i, 1/a_i, \dots, 1/a_i).
	\end{equation}
	This directly leads to
	\begin{align}
		H_\alpha(\Gamma_{\bma}(\w)) &= \frac{1}{1-\alpha} \log_2 \sum_{i=1}^N a_i \left( \frac{w_i}{a_i} \right)^\alpha \nonumber\\
		&= \frac{1}{1-\alpha} \log_2 \sum_{i=1}^N w_i^{\alpha} a_i^{1-\alpha} \nonumber\\
		&= \frac{1}{1-\alpha} \log_2 K^{1-\alpha} \sum_{i=1}^N w_i^{\alpha} r_i^{1-\alpha} \nonumber\\
		&= K + \frac{1}{1-\alpha} \log_2 \sum_{i=1}^N w_i^{\alpha} r_i^{1-\alpha} \nonumber\\
		&= K - D_\alpha(\w ||\r).
	\end{align}
\end{proof}

@@

1. We need to prove that
\begin{equation}
	\sum_{\bmx} W_{\tau}(\bmx) W_{\rho|\tau}(\x)^\alpha \geq 1.
\end{equation}
\nick{How do we do this, while respecting the constraints on $\alpha$?}

2. Assume $D_\alpha (\rho,\tau) = 0$.
Then,
\begin{equation}
	\sum_{\bmx} W_{\tau}(\bmx) W_{\rho|\tau}(\x)^\alpha = 1,
\end{equation}
\nick{so...}.
The converse holds by inspection.

3. This property follows from the multiplicativity of the WIgner distribution.
In particular,
\begin{align}
	&D_\alpha(\rho^{\otimes n} || \tau^{\otimes n}) = \nonumber\\
	&\frac{1}{\alpha - 1} \log_2 \sum_{\bmx} W_{\rho^{\otimes n}}(\bmx)^\alpha W_{\tau^{\otimes n}}(\bmx)^{1-\alpha} = \nonumber\\
	&\frac{1}{\alpha - 1} \log_2 \sum_{\bmx} \prod_{i=1}^n W_{\rho}(\bmx_i)^\alpha W_{\tau}(\bmx_i)^{1-\alpha} = \nonumber\\
	&\frac{1}{\alpha - 1} \log_2 \prod_{i=1}^n \sum_{\bmx_i} W_{\rho}(\bmx_i)^\alpha W_{\tau}(\bmx_i)^{1-\alpha} = \nonumber\\
	&\sum_{i=1}^n \frac{1}{\alpha - 1} \log_2 \sum_{\bmx'} W_{\rho}(\bmx')^\alpha W_{\tau}(\bmx')^{1-\alpha} = \nonumber\\
	&= n D_{\alpha}(\rho || \tau).
\end{align}

4. \nick{This must hold due to~\cref{thm:H2D}}
\end{proof}
\nick{Combining ALL the properties above (and nothing more) leads to the general bound}

@@

For the given form of $\alpha$, $H_{\alpha}$ is Schur-concave due to~\cref{thm:HSchur}, so
\begin{equation}
	H_{\alpha}(\Gamma_{\bma}(W_{\rho_n})) \leq H_{\alpha}(\Gamma_{\bma'}(W_{\rho'_{n'}})),
\end{equation}
and we can use~\cref{thm:H2D} to rewrite the inequality as
\begin{equation}
	K - D_{\alpha}(W_{\rho_n} || W_{\tau_n}) \leq K - D_{\alpha}(W_{\rho'_{n'}} || W_{\tau'_{n'}}),
\end{equation}.
Due to~\cref{thm:Da_props}, we can rewrite the inequality as
\begin{equation}
	K - nD_{\alpha}(W_{\rho} || W_{\tau}) \leq K - n'D_{\alpha}(W_{\rho'} || W_{\tau'}),
\end{equation}
and rearrange it to reach
\begin{equation}
	\frac{n'}{n} \leq \frac{D_{\alpha}(\rho||\tau)}{D_{\alpha}(\rho'||\tau')}.
\end{equation}
\end{proof}

@@

Conversely, suppose $\rho$ has negativity in its Wigner representation. This implies that $\sum_{\x} |W_\rho (\x)| >1$. We now consider $\sum_{\x} W_\rho (\x)^{a/b}$ for $a/b >1$ and $a$ even and $b$ odd. We have that
\begin{align}
\sum_{\x} W_\rho (\x)^{a/b} &= \sum_{\x} |W_\rho (\x)|^{a/b} \nonumber \\
&= \sum_{\x} |W_\rho (\x)|^{1+ \epsilon},
\end{align}
where $\epsilon = a/b - 1 >0$. By choosing $a$ and $b$ appropriately we can make $\epsilon$ arbitrarily close to $0$ and therefore there exists a sequence $\epsilon_n$ such that
\begin{equation}
\sum_{\x} |W_\rho (\x)|^{1+ \epsilon_n} \rightarrow \sum_{\x} |W_\rho (\x)| >1.
\end{equation}
Therefore, $H_\alpha (W_\rho (\x)) <0 $ at some point in the sequence, which completes the proof.
\end{proof}
Therefore Wigner negativity coincides with negativity in at least one Renyi entropy.
\ddd{[Looking at this limit it almost feels like the $\alpha \rightarrow 0^+$ limit is actually giving mana....modulo the technical problem of taking the limit without calculus. I will think more about this point.]}

\subsubsection{Extention to general relative majorization}
